---
title: "Quiz 1"
output: 
  html_document: 
    theme: spacelab
---
### Question 1
#### The R language is a dialect of which of the following programming languages?
* Lisp
* Scheme
* __S__
* Fortran

### Question 2
#### The definition of free software consists of four freedoms (freedoms 0 through 3). Which of the following is NOT one of the freedoms that are part of the definition? Select all that apply.
* __The freedom to restrict access to the source code for the software__
* The freedom to run the program, for any purpose.
* The freedom to study how the program works, and adapt it to your needs.
* The freedom to improve the program, and release your improvements to the public, so that the whole community benefits.
* The freedom to redsitribute copies so you can help your neighbor.
* __The freedom to prevent users from using the software for undesirable purposes.__
* __The freedom to sell the software for any price.__

### Question 3
#### In R the following are all atomic data types EXCEPT: (Select all that apply)
* complex
* __matrix__
* numeric
* logical
* __table__
* __list__
* character
* __data frame__
* __array__
* integer

### Question 4
#### If I execute the expression x<-4 in R, what is the class of the object 'x' as determined by the 'class()' function?
* matrix
* __numeric__
* complex
* list
* real
* vector
* integer
```{r}
x<-4
class(x)
```

### Question 5
#### What is the class of the object defined by the expression x<-c(4,"a",TRUE)?
* numeric
* integer
* logical
* __character__
* mixed
```{r}
x<-c(4,"a",TRUE)
class(x)
```

### Question 6
#### If I have two vectors x<-c(1,3,5) and y<- c(3,2,10), what is produced by the expression cbind(x,y)?
* a 2 by 2 matrix
* a 3 by 3 matrix
* a vector of length 2
* __a matrix with 2 columns and 3 rows__
* a vector of length 3
* a 2 by 3 matrix
```{r}
x<-c(1,3,5)
y<-c(3,2,10)
cbind(x,y)
```

### Question 7
#### A key property of vector in R is that
* elements of a vector can be of different clases
* a vector cannot have attributes like dimensions
* elements of a vector can only be character or numeric
* the length of a vector must be less than 32,768
* __ elements of a vector all must be of the same class__

### Question 8
#### Suppose I have a list defined as x<-list(2, "a", "b", TRUE). What does x[[1]] give me? Select all that apply.
* a list containing the number 2.
* a character vector containing the element "2".
* a list containing a numeric vector of length 1.
* __a numeric vector of length 1.__
* __a numeric vector containg the element 2.__
```{r}
x<-list(2,"a", "b", TRUE)
x[[1]]
class(x[[1]])
```

### Question 9
#### Suppose I have a vector x<-1:4 and y<-2:3. What is produced by the expression x+y?
* an integer vector with the values 3, 5, 3, 4.
* a numeric vector with the values 3, 5, 3, 4.
* a numeric vector with the values 3, 5, 5, 7.
* __an integer vector with the values 3, 5, 3, 7.__
* an error.
* a warning.
* a numeric vector with the values 1, 2, 5, 7.

```{r}
x<-1:4
y<-2:3
x+y
class(x+y)
```

### Question 10
#### Suppose I have a vector x<-c(3,5,1,10,12,6) and I want to set all elements of this vector that are less than 6 to be equal to zero. What R code achieves this? Select all that apply.
* x[x==0]<6
* x[x>=6]<-0
* x[x==6]<-0
* __x[x %in% 1:5]<-0__
* x[x>6]<-0
* x[x>0]<-6
* x[x<6]==0
* __x[x<=5]<-0__
* __x[x<6]<-0__
* x[x!=6]<-0
* x[x==0]<-6
```{r}
x<-c(3,5,1,10,12,6)
x[x %in% 1:5]<-0
x
x<-c(3,5,1,10,12,6)
x[x<=5]<-0
x
x<-c(3,5,1,10,12,6)
x[x<6]<-0
x
```

## Use the Week 1 Quiz Data Set to answer questions 11 - 20.

### Question 11
#### In the dataset provided for this Quiz, what are the column names of the dataset?
* 1, 2, 3, 4, 5, 6
* Ozone, Solar.R, Wind
* Month, Day, Temp, Wind
* __Ozone, Solar.R, Wind, Temp, Month, Day__
```{r}
hw1_data<-read.csv("Data_Sets/hw1_data.csv")
colnames(hw1_data)
```

## Question 12
#### Extract the first 2 rows of the data frame and print them to the console. What does the output look like?
```{r}
hw1_data[c(1,2),]
```

### Question 13
#### How many observations (i.e. rows) are in this data frame?
* 160
* __153__
* 45
* 129
```{r}
nrow(hw1_data)
```

### Question 14
#### Extract the last 2 rows of the data frame and print them to the console.What does the output look like?
```{r}
tail(hw1_data,2)
```

### Question 15
#### What is the value of Ozone in the 47th row?
* __21__
* 34
* 18
* 63

```{r}
hw1_data[47,"Ozone"]
```

### Question 16
#### How many missing values are in the Ozone column of this data frame?
* 78
* 43
* 9
* __37__
```{r}
na_Ozone=subset(hw1_data, is.na(Ozone))
nrow(na_Ozone)
```

### Question 17
#### What is the mean of the Ozone column in this dataset? Exclude missing values (coded as NA) from this calculation.
* __42.1__
* 18.0
* 31.5
* 53.2
```{r}
mean(hw1_data[,"Ozone"],na.rm=TRUE)
```

### Question 18
#### Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?
* 334.0
* __212.8__
* 185.9
* 205.0
```{r}
sub = subset(hw1_data, Ozone>31 & Temp>90)
mean(sub[,"Solar.R"], na.rm=TRUE)
```

### Question 19
#### What is the mean of "Temp" when "Month" is equal to 6?
* 75.3
* 90.2
* __79.1__
* 85.6
```{r}
june = subset(hw1_data, Month==6)
mean(june[,"Temp"], na.rm=TRUE)
```

### Question 20
#### What was the maximum ozone value in the month of May (i.e. Month is equal to 5)
* 97
* 18
* __115__
* 100
```{r}
may = subset(hw1_data, Month==5)
max(may[,"Ozone"],na.rm=TRUE)
```