---
title: "Quiz 2"
output: 
  html_document: 
    theme: spacelab
---
### Question 1
#### Suppose I define the following function in R. What is the result of running cube(3) in R after defining this function?
```{r}
cube<-function(x,n){
    x^3
}
```
* An error is returned because 'n' is not specified in the call to 'cube'.
* The users is prompted to specify the value of 'n'.
* A warning is given with no value returned.
* __The number 27 is returned.__
```{r}
cube(3)
```

### Question 2
#### The following code will produce a warning in R. Why?
```{r}
x<-1:10
if(x>5){
    x<-0
}
```
* The expression uses curly braces.
* The syntax of this R expression is incorrect.
* __'x' is a vector of length 10 and 'if' can only test a single logical statement.__
* You cannot set 'x' to be 0 because x is a vector and 0 is a scalar.
* There are no elements in 'x' that are greater than 5.

### Question 3
#### Consider the following function.
```{r}
f<- function(x){
    g<- function(y){
        y+z
    }
    z<-4
    x+g(x)
}
```
#### If I then run in R
```{r}
z<-10
f(3)
```
#### What value is returned?
* 16
* 4
* __10__
* 7

### Question 4
#### Consider the following expression. What is the value of y after evaluating this expression
```{r}
x <- 5
y <- if(x < 3) {
        NA
} else {
        10
}
```
* __10__
* 3
* NA
* 5
```{r}
y
```

### Question 5
#### Consider the following R function. Which symbol in the function is a free variable.
```{r}
h <- function(x, y = NULL, d = 3L) {
        z <- cbind(x, d)
        if(!is.null(y))
                z <- z + y
        else
                z <- z + f
        g <- x + y / z
        if(d == 3L)
                return(g)
        g <- g + 10
        g
}
```
* __f__
* z
* d
* L
* g

### Question 6
#### What is an environment in R?
* an R package that only contains data
* __a collection of symbol/value pairs__
* a special type of function
* a list whose elements are all functions

### Question 7
#### The R language uses what type of scoping frule for resolving free variables?
* global scoping
* __lexical scoping__
* compilation scoping
* dynamic scoping

### Question 8
#### How are free variables in R functions resolved?
* The values of free variables are searched for in the environment in which the function was called.
* __The values of free variables are searched for in the environment in which the function was defined.__
* The values of free variables are searched for in the global environment.
* The values of free variables are searched for in the working directory.

### Question 9
#### What is one of the consequences of the scoping rules used in R?
* R objects cannot be larger than 100 MB.
* Functions cannot be nested.
* __All objects must be stored in memory.__
* All objects can be stored on the disk.

### Question 10
#### In R, what is the parent frame?
* It is always the global environment
* It is the package search list
* It is the environment in which a function was defined
* __It is the environment in which a function was called__